\textls[-0]{\thetitle}

### 2023-03-18 syn-translate.tex
remove gratuitous parens
edits
Rewrite syn-translate. Please review

We first define a new type $\goodType{\Gamma}{\Sigr{\Gamma}{n}{j}}{}$  when
$\goodCtx{\Gamma}{}$  is well-formed and $n \in \mathbb{N}$
such that $\goodTerm{\Gm}{\denotesT{\goodSigU{j}{\Gamma}{\lsig}{n}}}{\Sigr{\Gm}{n}{j}}$.
We make $({\Sigr{\Gamma}{n}{}})$ and $\denotesT{\TyTkg {-}}$ mutually recursive,
defined by induction on $n$ and the signature length.
% \denotesT{\goodSig{\Gamma}{\_}{n}} &= (\goodTerm{\Gamma}{\_}{\Sigr{\Gamma}{n}}) \\ 
% &\text{, and thus } \denotesT{\goodSig{\Gamma}{\sigma}{n}} \text{ defined} \iff \goodTerm{\Gamma}{\denotesT{\sigma}}{\Sigr{\Gamma}{n}} \\

\begin{align*}
  {\Sigr{\Gamma}{(n+1)}{j}} &= 
    \Sigma~(\Sigr{\Gamma}{n}{j})
          ~(\Sigma~\cU_j \\
          & \quad \quad ~(\Sigma~(\TyPi{\denotesT{\TyTkg {\sub{\var{0}}{\SubstWeak{1}}}}}{\El{\sub{\var{0}}{\SubstWeak{1}}}}) \\
          & \quad \quad \quad \TyPi{\El{\sub{\var{0}}{\SubstWeak{1}}}}{\cU_j})) \\
  \Sigr{\Gamma}{0}{j} &= \top \\
  \denotesT{\goodType{\Gamma}{\TyTkg {\sigma}}{}}, \denotesT{\goodType{\Gamma}{\TyLkg{\sigma}}{}} &\text{ defines upon } \denotesT{\sigma} 
  \text{ and inductively on the signature length} \\
  \denotesT{\goodType{\Gamma}{\TyTkg {\sigma}}{}} &= \denotesT{\goodType{\Gamma}{\TyLkg{\sigma}}{}} = \top \quad
      \text{given } \denotesT{\goodSig{\Gamma}{\sigma}{0}} \\
  \denotesT{\goodType{\Gamma}{\TyTkg {\sigma}}{}} &= 
    \Sigma~\denotesT{\TyTkg {\lsigproj{1}{\sigma}}}~(\El{\app{"snd"^3~\denotesT{\sigma}}[(\SubstWeak{1}, \app{\fst{("snd"^2~{\denotesT{\sigma}})}})]}) \\
  \denotesT{\goodType{\Gamma}{\TyLkg{\sigma}}{}} &=
  \denotesT{\TyLkg{\lsigproj{1}{\sigma}}} \times \Pi(\El{\fst{(\snd{\denotesT{\sigma}})}})(\El{\app{"snd"^3~\denotesT{\sigma}}}) \\
  &\text{given } \denotesT{\goodSig{\Gamma}{\sigma}{n+1}} \\
  \denotesT{\goodSigU{j}{\Gamma}{\LSigEmp}{0}} &= \unit \\
  \denotesT{\goodSigU{j}{\Gamma}{\LSigAdd{\sigma}{f}{T}}{n+1}} &= (\denotesT{\sigma}, \codety{A}, \lam{f}, \lam{\codety{T}}) \\
  \denotesT{\goodTerm{\Gamma}{\LkgEmp}{\TyLkg{\LSigEmp}}} &= \unit \\
  \denotesT{\goodTerm{\Gamma}{\mu^+~m~t}{\TyLkg{\LSigAdd{\sigma}{s}{T}}}} &= (\denotesT{m}, \lam{t}) \\
  \denotesT{\goodTerm{\Gamma}{\Tkg{m}}{\TyTkg {\sigma}}} & \text{ is defined upon } \denotesT{m} \text{ and inductively on the signature length} \\
  \denotesT{\goodTerm{\Gamma}{\Tkg {m}}{\TyTkg {\sigma}}} &= () \quad \text{given } \denotesT{\goodSig{\Gamma}{\sigma}{0}} \\
  \denotesT{\goodTerm{\Gamma}{\Tkg {m}}{\TyTkg {\sigma}}} &= 
  (\denotesT{\Tkg {o}}, t[(\SubstExt{p^1}{f})][(\SubstExt{"id"}{\denotesT{\Tkg {o}}})]) \\
  & \text{given } \denotesT{\goodSig{\Gamma}{\sigma}{n+1}}, \text{ where } o = \lsigproj{1}{m}, t = \app{\snd{\denotesT{m}}}, f = p_f\nu~\sigma 
\end{align*}
% \begin{align*}
%   \denotesT{\goodInh{\Gamma}{\_}{\sigma_1}{\sigma_2}} &= \goodTerm{\Gamma, \TyLkg{\sigma_1}}{\_}{\TyLkg{\sigma_2[p^1]}} \\ \text{ and thus } \denotesT{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}} &\iff  \goodTerm{\Gamma, \TyLkg{\sigma_1}}{h}{\TyLkg{\sigma_2[p^1]}} \\
%   \denotesT{\goodInh{\Gamma}{"inhinh"~h~T~\uparrow^s}{(\LSigAdd {\sigma_1} {s_1}{T})}{(\LSigAdd {\sigma_2} {s_2} {T[(p^1, \uparrow^s)]})}} &= \mu^+~(h[(p^1,\lkgproj{1}{"var"_0})])\\ &\quad \quad \{f_2[p^1]\}~(\lkgproj{2}{"var"_0})[(p^1, \uparrow^s[{p^1}^{\uparrow}])] \\
% \end{align*}

>>>>

We will first define two helpers
\begin{itemize}
  \item a new type $\goodType{\Gamma}{\Sigr{\Gamma}{n}{j}}{}$  when
  $\goodCtx{\Gamma}{}$  is well-formed and $n \in \mathbb{N}$
  such that $\goodTerm{\Gm}{\denotesT{\goodSigU{j}{\Gamma}{\lsig}{n}}}{\Sigr{\Gm}{n}{j}}$
  \item and a function $\mathscr{P} : \{\lsig' : \goodTerm{\Gm}{\lsig'}{\Sigr{\Gm}{n}{j}} \} \to \{ T : \goodType{\Gm}{T}{} \}$ map one syntax term of $\Sigr{\Gm}{n}{j}$ into a type.
\end{itemize}
mutually inductively on $n$, the signature length.

\begin{align*}
  {\Sigr{\Gamma}{(n+1)}{j}} &= 
    \Sigma~(\Sigr{\Gamma}{n}{j})
          ~(\Sigma~\cU_j \\
          & \quad \quad ~(\Sigma~(\TyPi{{\mathscr{P}({\sub{\var{0}}{\SubstWeak{1}}})}}{\El{\sub{\var{0}}{\SubstWeak{1}}}}) \\
          & \quad \quad \quad \TyPi{\El{\sub{\var{0}}{\SubstWeak{1}}}}{\cU_j})) \\
  \Sigr{\Gamma}{0}{j} &= \top \\
  \mathscr{P}(\lsig') &=  \top \quad \text{ when } \goodTerm{\Gm}{\lsig'}{\Sigr{\Gm}{0}{j}}  \\
  \mathscr{P}(\lsig') &=  
    \Sigma~(\fst{\lsig'})~(\El{\app{"snd"^3~\lsig'}[(\SubstWeak{1}, \app{\fst{("snd"^2~{\lsig'})}})]}) \\ & \text{ when } \goodTerm{\Gm}{\lsig'}{\Sigr{\Gm}{n+1}{j}} \\
\end{align*}

% We make $({\Sigr{\Gamma}{n}{}})$ and

% $\denotesT{\TyTkg {-}}$ mutually recursive,
% defined by induction on $n$ and the signature length.
% \denotesT{\goodSig{\Gamma}{\_}{n}} &= (\goodTerm{\Gamma}{\_}{\Sigr{\Gamma}{n}}) \\ 
% &\text{, and thus } \denotesT{\goodSig{\Gamma}{\sigma}{n}} \text{ defined} \iff \goodTerm{\Gamma}{\denotesT{\sigma}}{\Sigr{\Gamma}{n}} \\

With the above two helpers, we can define denotation $\denotesT{}$.

\begin{align*}
  \denotesT{\goodSigU{j}{\Gamma}{\lsig}{n}} &\in \{t : \goodTerm{\Gm}{t}{\Sigr{\Gm}{n}{j}} \} \\
  {\goodType{\Gamma}{\TyTkg{\lsig}}{}} &= \mathscr{P}(\denotesT{\lsig}) \\
  \denotesT{\goodType{\Gamma}{\TyLkg{\sigma}}{}} &\text{ defines upon } \denotesT{\lsig} 
  \text{ and inductively on the signature length} \\
  \denotesT{\goodType{\Gamma}{\TyLkg{\sigma}}{}} &=
  \denotesT{\TyLkg{\lsigproj{1}{\sigma}}} \times \Pi(\El{\fst{(\snd{\denotesT{\sigma}})}})(\El{\app{"snd"^3~\denotesT{\sigma}}}) \\
  &\text{given } \denotesT{\goodSig{\Gamma}{\sigma}{n+1}} \\
  \denotesT{\goodType{\Gamma}{\TyLkg{\sigma}}{}} &= \top \quad
  \text{given } \denotesT{\goodSig{\Gamma}{\sigma}{0}} \\
  \denotesT{\goodSigU{j}{\Gamma}{\LSigEmp}{0}} &= \unit \\
  \denotesT{\goodSigU{j}{\Gamma}{\LSigAdd{\sigma}{f}{T}}{n+1}} &= (\denotesT{\sigma}, \codety{A}, \lam{f}, \lam{\codety{T}}) \\
  \denotesT{\goodTerm{\Gamma}{\LkgEmp}{\TyLkg{\LSigEmp}}} &= \unit \\
  \denotesT{\goodTerm{\Gamma}{\mu^+~m~t}{\TyLkg{\LSigAdd{\sigma}{s}{T}}}} &= (\denotesT{m}, \lam{t}) \\
  \denotesT{\goodTerm{\Gamma}{\Tkg{m}}{\TyTkg {\sigma}}} & \text{ is defined upon } \denotesT{m} \text{ and inductively on the signature length} \\
  \denotesT{\goodTerm{\Gamma}{\Tkg {m}}{\TyTkg {\sigma}}} &= () \quad \text{given } \denotesT{\goodSig{\Gamma}{\sigma}{0}} \\
  \denotesT{\goodTerm{\Gamma}{\Tkg {m}}{\TyTkg {\sigma}}} &= 
  (\denotesT{\Tkg {o}}, t[(\SubstExt{p^1}{f})][(\SubstExt{"id"}{\denotesT{\Tkg {o}}})]) \\
  & \text{given } \denotesT{\goodSig{\Gamma}{\sigma}{n+1}}, \text{ where } o = \lsigproj{1}{m}, t = \app{\snd{\denotesT{m}}}, f = p_f\nu~\sigma 
\end{align*}
% \begin{align*}
%   \denotesT{\goodInh{\Gamma}{\_}{\sigma_1}{\sigma_2}} &= \goodTerm{\Gamma, \TyLkg{\sigma_1}}{\_}{\TyLkg{\sigma_2[p^1]}} \\ \text{ and thus } \denotesT{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}} &\iff  \goodTerm{\Gamma, \TyLkg{\sigma_1}}{h}{\TyLkg{\sigma_2[p^1]}} \\
%   \denotesT{\goodInh{\Gamma}{"inhinh"~h~T~\uparrow^s}{(\LSigAdd {\sigma_1} {s_1}{T})}{(\LSigAdd {\sigma_2} {s_2} {T[(p^1, \uparrow^s)]})}} &= \mu^+~(h[(p^1,\lkgproj{1}{"var"_0})])\\ &\quad \quad \{f_2[p^1]\}~(\lkgproj{2}{"var"_0})[(p^1, \uparrow^s[{p^1}^{\uparrow}])] \\
% \end{align*}
